### 2015-07-07 doc/thesis/review.tex
Moving statistics summary into a table

We end this chapter presenting a summary of the statistics that
we just presented:
\begin{itemize}
\item table constructor
\begin{itemize}
\item only use literal keys: 73\%
\item empty: 26\%
\item only use non-literal keys: 1\%
\end{itemize}
\item table indexing
\begin{itemize}
\item reads: 86\%
\begin{itemize}
\item use literals: 93\%
\item use non-literals: 7\%
\end{itemize}
\item writes: 14\%
\begin{itemize}
\item use literals: 71\%
\item use non-literals: 29\%
\end{itemize}
\end{itemize}
\item iteration over tables
\begin{itemize}
\item files that call \texttt{pairs}: 23\%
\item files that call \texttt{ipairs}: 21\%
\item files that use the numeric for along with the length operator: 10\%
\end{itemize}
\item function declarations
\begin{itemize}
\item perform dynamic type checking in their input parameters: 9\%
\begin{itemize}
\item asserting input parameters: 50\%
\item overloading input parameters: 50\%
\end{itemize}
\item return multiple values: 10\%
\begin{itemize}
\item return \texttt{nil} plus something else: 50\%
\item return \texttt{false} plus something else: 10\%
\item return other multiple values: 40\%
\end{itemize}
\item are method declarations: 23\%
\item are variadic: 8\%
\end{itemize}
\item object-oriented programming
\begin{itemize}
\item projects that extend metatables and declare methods: 45\%
\end{itemize}
\item modules
\begin{itemize}
\item files that define modules: 61\%
\item files that are plain scripts: 39\%
\end{itemize}
\end{itemize}

>>>>

Table \ref{tab:statistics} summarizes the statistics that we presented in this section.

\begin{table}[!ht]
\begin{center}
\begin{tabular}{|l|p{6cm}|c|}
\hline
\multirow{5}{*}{table constructor}
& create a record & 36\% \\
\cline{2-3}
& create a list & 29\% \\
\cline{2-3}
& create an empty table & 26\% \\
\cline{2-3}
& create a table with a record part and a list part & 8\% \\
\cline{2-3}
& create a table with non-literal keys & 1\% \\
\hline
\multirow{4}{*}{table access}
& reading with literal keys & 80\% \\
\cline{2-3}
& writing with literal keys & 10\% \\
\cline{2-3}
& reading with non-literal keys & 6\% \\
\cline{2-3}
& writing with non-literal keys & 4\% \\
\hline
\multirow{2}{*}{iteration over tables} &
files that iterate over a list & 27\% \\
\cline{2-3}
& files that iterate over a map & 23\% \\
\hline
\multirow{4}{*}{function declarations}
& inspect the tags of their input parameters & 9\% \\
\cline{2-3}
& return multiple values to signal errors & 6\% \\
\cline{2-3}
& are variadic & 8\% \\
\cline{2-3}
& are method declarations & 23\% \\
\hline
\multirow{1}{*}{object-oriented programming}
& projects that use metatables and declare methods & 45\% \\
\hline
\multirow{2}{*}{modules}
& files that are modules & 61\% \\
\cline{2-3}
& files that are plain scripts & 39\% \\
\hline
\end{tabular}
\end{center}
\caption{Summary of the statistics about the usage of Lua}
\label{tab:statistics}
\end{table}
